Meta RL analyses

### 2018-11-14 meta_RL_analyses.Rmd
plot of swept meta batch sizes

```{r}
library(tidyverse)
```

```{r}
num_runs = 20
results_dir = "results/paper_results/"

result_subdirs = c("basic", "nometa", "basic_su_heldout", "nometa_su_heldout")

@@

@@

reward_d = reward_d %>%
  mutate(is_su_ho=grepl("su_heldout", run_type)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = (!is_su_ho & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout))
```

@@

# meta mapping (true) evaluation

>>>>

```{r}
library(tidyverse)
library
```

```{r}
num_runs = 1
results_dir = "results/paper_results/"

result_subdirs = c("nometa")#, "nometa_su_heldout", "nometa_random_holdout",
                   #"basic", "basic_su_heldout", "basic_random_holdout")

@@

new_game_strs_random_heldout = c('game_match_l_0_bv_0_sr_1', 'game_match_l_0_bv_1_sr_1', 'game_pairs_and_high_l_1_bv_1_sr_0', 'game_high_card_l_0_bv_1_sr_1', 'game_straight_flush_l_1_bv_0_sr_1', 'game_straight_flush_l_0_bv_0_sr_0', 'game_pairs_and_high_l_0_bv_1_sr_1', 'game_straight_flush_l_1_bv_0_sr_0', 'game_match_l_1_bv_0_sr_1', 'game_pairs_and_high_l_0_bv_1_sr_0', 'game_pairs_and_high_l_1_bv_0_sr_0', 'game_sum_under_l_1_bv_0_sr_0', 'game_sum_under_l_0_bv_1_sr_0', 'game_high_card_l_1_bv_0_sr_1', 'game_sum_under_l_0_bv_0_sr_0', 'game_pairs_and_high_l_0_bv_0_sr_1', 'game_sum_under_l_1_bv_0_sr_1', 'game_match_l_1_bv_1_sr_1', 'game_sum_under_l_0_bv_1_sr_1', 'game_straight_flush_l_1_bv_1_sr_1')

@@

reward_d = reward_d %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_random_ho=grepl("random", run_type)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = (!is_random_ho & !is_su_ho & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) )
```

@@

## sweeping batch sizes
```{r}
sweep_d = load_d(results_dir, result_subdirs, num_runs, "new_sweep_rewards")

sweep_d = sweep_d %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_random_ho=grepl("random", run_type)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = (!is_random_ho & !is_su_ho & game_str %in% new_game_strs) | (is_su_ho & game_str %in% new_game_strs_su_heldout) | (is_random_ho & game_str %in% new_game_strs_random_heldout) )
```

```{r}
avg_sweep_d = sweep_d %>%
  select(-game_str) %>%
  filter(epoch == 0) %>%
  group_by(run_type, size, game_type, is_new_game) %>%
  summarize(avg_reward = mean(reward), sd_reward=sd(reward),
            se_reward = sd_reward/sqrt(n()), 
            ci_lo = avg_reward - 1.96*se_reward, 
            ci_hi = avg_reward + 1.96*se_reward)
```

```{r}
ggplot(avg_sweep_d, aes(x=size, color=is_new_game, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set2") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ run_type)
```
# meta mapping (true) evaluation
